analyze_growth

### 2023-03-17 recaps.Rmd

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
load("Recaps.RData")
```

@@

recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft.xlsx", 
                    sheet = "Adult Recaptures") %>%
  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)
recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
                Type = case_when(Type == "header" ~ "Soft",
                                 TRUE ~ Type))
str(recaps)

@@

recapsf = st_as_sf(filter(recaps, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)

#Now make a data frame of the release locations
release = data.frame(Site = c("SDWSC", "SDWSC", "Rio Vista", "Rio Vista"), Type = c("Soft", "Hard", "Hard", "Hard (Trailer)"),
                     Latitude = c(38.237842, 38.275563, 38.124736, 38.139752), 
                     Longitude = c(-121.673802, -121.661374, -121.699521, -121.694706)) 
releasesf = st_as_sf(release,  coords = c("Longitude", "Latitude"), crs = 4326)

@@

recaps2 = left_join(recaps, release)

@@

```{r, eval=FALSE}
#one release at a time
Dwschard = filter(recaps2, Type == "Hard", Site == "SDWSC")
dwsch = filter(release, Site == "SDWSC", Type == "Hard") %>%
  select(Latitude, Longitude)
tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwsch)

#now let's do DWSC soft
Dwscsoft = filter(recaps2, Type == "Soft", Site == "SDWSC")
dwscs = filter(release, Site == "SDWSC", Type == "Soft") %>%
  select(Latitude, Longitude)
tesst2 = GGdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwscs)

#now let's do Rio Vista hard
RVhard = filter(recaps2, Type == "Hard", Site == "Rio Vista", !is.na(Latitude))
rvh = filter(release, Site == "Rio Vista", Type == "Hard") %>%
  select(Latitude, Longitude)
tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvh)

#now the trailer
RVhardt = filter(recaps2, Type == "Hard (Trailer)", Site == "Rio Vista")
rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
  select(Latitude, Longitude)
tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvht)

@@

Plot to visually look at mean and variatoin.

@@

Cluster = data.frame(Release = c("RV Hard", "RV Hard Trailer", "DWSC hard", "DWSC soft"),
                     meadist = c(mean(RVhdistx), mean(RVhdist), mean(SCsoft), mean(SChard)),
                     SD = c(sd(RVhdistx), sd(RVhdist), sd(SCsoft), sd(SChard)))
Cluster = mutate(Cluster, CV = SD/meadist)
Cluster
```

>>>>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
#load("Recaps.RData")
```

@@

recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft.xlsx", 
                    sheet = "Adult Recaptures") %>%
  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)

recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
                Type = case_when(Type == "header" ~ "Soft",
                                 TRUE ~ Type)) %>%
  rename(Adclip = `Ad clip`, Mark = `VIE Color/Position`) %>%
  select(-Type, -Site)
str(recaps)

@@

#Now make a data frame of the release locations
release = read_excel("releases.xlsx") %>%
  rename(LatitudeR = Latitude, LongitudeR = Longitude)
releasesf = st_as_sf(filter(release, !is.na(LatitudeR)),  coords = c("LongitudeR", "LatitudeR"), crs = 4326)

@@

recaps2 = left_join(recaps, release) %>%
  mutate(DaysSinceRelease = Date - ReleaseDate)
recapsf = st_as_sf(filter(recaps2, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)

@@

```{r, eval=FALSE}
#one release at a time
Dwschard = filter(recaps2, Type == "Hard", Site == "SDWSC")
dwsch = filter(release, Site == "SDWSC", Type == "Hard") %>%
  select(LatitudeR, LongitudeR) %>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwsch)

#now let's do DWSC soft
Dwscsoft = filter(recaps2, Type == "Soft", Site == "SDWSC")
dwscs = filter(release, Site == "SDWSC", Type == "Soft") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst2 = GGdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwscs)

#now let's do Rio Vista hard
RVhard = filter(recaps2, Type == "Hard", Site == "Rio Vista", !is.na(Latitude))
rvh = filter(release, Site == "Rio Vista", Type == "Hard") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvh)

#now the trailer
RVhardt = filter(recaps2, Type == "Hard (Trailer)", Site == "Rio Vista")
rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvht)

@@

Plot to visually look at mean and variation.

@@

Cluster = data.frame(Release = c("RV Hard", "RV Hard Trailer", "DWSC soft", "DWSC hard"),
                     meadist = c(mean(RVhdistx[lower.tri(RVhdistx)]), 
                                 mean(RVhdist[lower.tri(RVhdist)]), 
                                 mean(SCsoft[lower.tri(SCsoft)]), 
                                 mean(SChard[lower.tri(SChard)])),
                     SD = c(sd(RVhdistx), sd(RVhdist), sd(SCsoft), sd(SChard)))

Cluster = mutate(Cluster, CV = SD/meadist)
Cluster
```

OK, now how to I put these all together to graph them?

RVhdistx[lower.tri(RVhdistx, diag = T)] = NA
RVhdist[lower.tri(RVhdist, diag = T)] = NA
SCsoft[lower.tri(SCsoft, diag = T)] = NA
SChard[lower.tri(SChard, diag = T)] = NA
RVdtx = as.data.frame(RVhdistx) %>%
  mutate(Fish1 = row.names(RVhdistx)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "Rio Vista Hard")

RVdt = as.data.frame(RVhdist) %>%
  mutate(Fish1 = row.names(RVhdist)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "Trailer")

SCs = as.data.frame(SCsoft) %>%
  mutate(Fish1 = row.names(SCsoft)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "DWSC Soft")

SCh = as.data.frame(SChard) %>%
  mutate(Fish1 = row.names(SChard)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "DWSC Hard")

nndist = bind_rows(RVdtx, RVdt, SCs, SCh)

ggplot(nndist, aes(x = Release, y = Distance, fill = Release)) + geom_boxplot()+
  ylab("Distance Between Recaptures")

Now let's bring in the time aspect

recapstime = read_excel("RecapturesSummary_1.xlsx", sheet = "REcapture Distances")

### 2023-03-17 smelt_2019_allseasons/Zoop 2019.Rmd

---
librarytitle: "Zoop Plotting"
output: html_document
editor_options: 
  chunk_output_type: console
---
# load packages
```{r}
library(tidyverse)
library(lubridate)
library(Polychrome)
library(here)
```

@@

#zoop <- read_csv("smelt_2019_allseasons/data_raw/ZoopData_SummerFall_2019.csv")
zoop <- read_csv("data_raw/ZoopData_SummerFall_2019.csv")

@@

#bring in tow data
#aug <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
#oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
aug <- read_csv("data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
oct <- read_csv("data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")

@@

#remove 0's
caught <- all[!(all$ind_m3==0),]

@@

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

@@

#winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
winter <- read_csv("data_clean/zoop_abundance.csv")

@@

#remove throw samples
winter <- winter[!(winter$Method=="Throw"),]

#merge with catch df
#condense to columns of interest
winter2 <- winter[c(1,2,13,27,30,22,23)]
caught2 <- caught[c(1,2,7,10,20,29,30)]

#rename column
winter2 <- winter2 %>% rename(ID = "Taxon")

#change ostracod taxa
winter2[winter2$ID %in% c("Ostracods"),]$Taxa <- "Ostracod"

@@

caught.sea <- caught.19 %>% 
  group_by(Season, Location, Taxa) %>% 
  summarize("sum.count"= sum(samplecount))

@@

library(vegan)
source("../PlotNMDS.R")

@@

@@

```{r}
#diet2 <- read_csv("smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
diet2 <- read_csv("data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all

@@

>>>>

---
librarytitle: "Zoop Plotting"
output: html_document
editor_options: 
  chunk_output_type: console
---
# load packages
```{r}
library(tidyverse)
library(lubridate)
library(Polychrome)
library(zooper)
```

@@

zoop <- read_csv("smelt_2019_allseasons/data_raw/ZoopData_SummerFall_2019.csv")
#zoop <- read_csv("data_raw/ZoopData_SummerFall_2019.csv")

@@

#bring in tow data
aug <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
aug <- read_csv("data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
oct <- read_csv("data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")

@@

#remove 0's
caught <- all[!(all$ind_m3==0),]
biomass = read_csv("zooptaxa.csv")
caught = left_join(caught, biomass) %>%
  mutate(bio_m3 = Mass*ind_m3)

@@

#First to CPUE
ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=ind_m3, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

#now try BPUE
ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Biomass of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

@@

winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
winter <- read_csv("data_clean/zoop_abundance.csv")

@@

#remove throw samples
winter <- winter[!(winter$Method=="Throw"),]
#change ostracod taxa
winter[winter$Taxon %in% c("Ostracods"),]$Taxa <- "Ostracod"
#merge with catch df
#condense to columns of interest
winter2 <- winter %>%
  rename(ID = Taxon) %>%
  select(Location, Date, Taxa, samplecount, ind_m3, bio_m3, Day, Month, MD) %>%
  group_by(Location, Date, Taxa, Day, Month, MD) %>%
  summarize(ind_m3 = sum(ind_m3), bio_m3 = sum(bio_m3))

caught2 <- caught %>%
  select(Location, Date, Taxa, samplecount, ind_m3, bio_m3, Day, Month, MD) %>%
  group_by(Location, Date, Taxa, Day, Month, MD) %>%
  summarize(ind_m3 = sum(ind_m3), bio_m3 = sum(bio_m3))

#rename column
#winter2 <- winter2 %>% rename(ID = "Taxon")

@@

caught.sea <- caught.19 %>% 
  group_by(Season, Location, Taxa) %>% 
  summarize(sum.count= sum(ind_m3))

@@

library(vegan)
source("PlotNMDS.R")

@@

#Britt and Bruce wanted biomass instead of abundance

zoopsBM = mutate(caught.19, SampleID = paste(Location, Date)) %>%
  filter(Taxa != "Microzoo") %>%
  pivot_wider(id_cols = c(SampleID, Location, Date, MD, Season), names_from = Taxa, values_from = bio_m3, values_fn = sum, values_fill = 0) %>%
  mutate(datatype = "Zoops")

#first let's look at Rio Vista across seasons
RVzoopsBM = filter(zoopsBM, Location == "RV")

#raw abundance matrix
RVzoopmatBM = as.matrix(RVzoopsBM[,6:11])

#relative abundance matrix
RVzoopmat2BM = RVzoopmatBM/rowSums(RVzoopmatBM)

RVa2 = adonis2(RVzoopmatBM~Season, data = RVzoopsBM)
RVa2
#

@@

```{r}
diet2 <- read_csv("smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
diet2 <- read_csv("data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all

@@

Can I do a permanova that takes date and location into accoutn?

zda = adonis2(zoopdietmat2 ~ datatype*Season + Location, strata = zoopdiet$Location, data = zoopdiet)
zda

zda1 = adonis2(zoopdietmat2 ~ datatype*Season + Location,data = zoopdiet)
zda1

with(zoopdiet, adonis2(zoopdietmat2 ~ datatype+ Season , strata = Location, data = zoopdiet, permutations = 199))

with(zoopdiet, adonis2(zoopdietmat2 ~ datatype+ Season +Location, strata = Season, data = zoopdiet, permutations = 199))
